\ProjectName{}: Data Imputation as a Query Optimization

### 2016-12-15 paper/experiments.tex
paper: switch to percentage change in error

\begin{table}
  \centerfloat
  \input{runtimes}
    \caption{Base error, change in error and and running time for queries
    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query run on clean
    data and the query run on dirty data without imputation. Change in error is relative to the base error.}
  \label{fig:experiments}
\end{table}

@@

Finally, we performed CE-CART imputation on the entirety of the ACS table, in order to compare our system to the traditional, pre-processing approach to imputation.
We were unable to complete the full imputation due to resource constraints, but the process ran for more than one hour without terminating.
This time compares favorably to our maximum of 55 seconds for a query with imputation on the ACS data.
Given the varying needs of database users, \ProjectName{} clearly allows flexibility without a significant performance hit.

>>>>

\begin{table}
  \centerfloat
  \input{runtimes}
    \caption{Base error, percent change in error and and running time for queries
    with different imputation levels. Base error is the root-mean-square error (RMSE) between the query run on clean
    data and the query run on dirty data without imputation. Change in error is relative to the base error.}
  \label{fig:experiments}
\end{table}

@@

Finally, we performed CE-CART imputation on the entirety of the ACS table, in order to compare our system to the traditional, pre-processing approach to imputation.
We were unable to complete the full imputation due to resource constraints, but the process ran for more than one hour without terminating.
This time compares favorably to our maximum of 72 seconds for a query with imputation on the ACS data.
Given the varying needs of database users, \ProjectName{} clearly allows flexibility without a significant performance hit.
